---
title: "Color and topic distributions"
author: "Nathanael Aff"
output: 
  html_document:
    code_folding: hide
---


<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk(here::here("code", "chunk-options.R"))
devtools::load_all()
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, nclude=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->


## Color distributions by topic

The last thing we'll look at before presenting plots for the final model is the color distribution over each topic. This gives us a picture of what our color themes actually are! 

```{r setup, }
library(dplyr)
library(purrr)
library(ggplot2)
```

```{r load-data, echo = FALSE, cache = TRUE}
load_data(sample_data = FALSE)
```

```{r load-chunk}
knitr::read_chunk(here::here("code", "compare-models.R"))
```

## Color distributions over topics 

For these plots the distribution is represented by a weighted relevance score (the same that is used in the `LDAvis` package). 


```{r color-distribution}
```

Even though our model scores might have leaned towards a model with fewere topics, we can see specific topics where adding more models separates themes that appear to be quite different. The firs two examples are of topic \# 2 from the 30 topic model which seems more coherent in the 40 topic model (the sencond plot). 


### Topic 2 from the 30 topic model

```{r  topic-waffle-2-2}
```

```{r topic-table-2-2}
```


### Topic 2 from the 40 topic model

```{r, topic-waffle-3-2}
```

```{r  topic-table-3-2}
```

One final plot from topic 32 that I looked questionable but seems to have grouped some related (if small) sets. 

```{r topic-waffle-3-32}
```


```{r topic-table-3-32}
```






